\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2010-11-09 doc/USER_MANUAL/manual_SPECFEM3D.tex
updated the list of authors and the manual

The SPECFEM3D package was first developed by Dimitri Komatitsch and Jeroen Tromp at Harvard University, then Caltech and Princeton, USA, starting in 1998, based in part on earlier work by Dimitri Komatitsch and Jean-Pierre Vilotte at IPG in Paris, France from 1994 to 1997. Since then it has been developed and maintained by a development team: in alphabetical order, C\'eline Blitz, Emiljana Jorgji, Dimitri Komatitsch, Nicolas Le Goff, Pieyre Le Loher, Roland Martin, David Mich\'ea, Jeroen Tromp \toall{add full list of developers here}.

@@

In the main directory type `\texttt{make meshfem3D}'. If all paths and flags
have been set correctly, the mesher should now compile and produce
the executable \texttt{bin/xmeshfem3D}.

@@

%% \section{Checking the MPI Buffers (Optional)}

%% The mesher writes MPI communication tables in the \texttt{OUTPUT\_FILES}
%% subdirectory in the files \texttt{addressing.txt}, \texttt{list\_messages\_corners.txt}
%% and \texttt{list\_messages\_faces.txt}, and MPI communication buffers
%% to the local disks. Use the four serial codes

%% \begin{lyxcode}
%% check\_buffers\_2D.f90

%% check\_buffers\_1D.f90
%% \end{lyxcode}
%% to check that all the MPI buffers created by the mesher have been
%% generated correctly. For example, typing `\texttt{make check\_buffers\_2D}'
%% and then `\texttt{xcheck\_buffers\_2D}' checks the communication buffers
%% between faces common to the mesh slices.

%% \begin{quote}
%% Please note that running these codes is optional because no information
%% needed by the solver is generated.
%% \end{quote}

%%\section{\label{sec:quality}Checking the Mesh Quality (Optional)}

@@

In the main directory type '\texttt{make generate\_databases}'. Input for the program is provided through the main parameter file \texttt{Par\_file}, which resides in the subdirectory \texttt{in\_data\_files/}. Before running \texttt{xgenerate\_databases}, a number of parameters need to be set in the \texttt{Par\_file}:

@@

Now that you have successfully generated the databases, you are ready to compile
the solver. In the main directory type `\texttt{make specfem3D}'.
%obsolete
%For reasons of speed, the solver uses static memory allocation.
%Therefore it needs to be recompiled (type `\texttt{make clean}' and
%`\texttt{make specfem3D}') every time one reruns \texttt{xgenerate\_databases}. To compile
%the solver one needs a file created by \texttt{xgenerate\_databases} in the directory
%\texttt{OUTPUT\_FILES} called \texttt{values\_from\_mesher.h}, which
%contains parameters describing the static size of the arrays as well
%as the setting of certain flags.

>>>>

The SPECFEM3D package was first developed by Dimitri Komatitsch and Jeroen Tromp at Harvard University, then Caltech and Princeton, USA, starting in 1998, based in part on earlier work by Dimitri Komatitsch and Jean-Pierre Vilotte at IPG in Paris, France from 1994 to 1997. Since then it has been developed and maintained by a development team: in alphabetical order, C\'eline Blitz, Emiljana Jorgji, Dimitri Komatitsch, Nicolas Le Goff, Pieyre Le Loher, Roland Martin, David Mich\'ea, Jeroen Tromp \toall{add full list of developers here and update the AUTHORS file accordingly}.

@@

In the main directory type `\texttt{make meshfem3D}'. If all paths and flags
have been set correctly, the mesher should now compile and produce
the executable \texttt{bin/xmeshfem3D}. Please note that  
\texttt{xmeshfem3D} must be called directly from the \texttt{bin/} directory, 
as most of the binaries of the package.

@@

@@

In the main directory type '\texttt{make generate\_databases}'. Input for the program is provided through 
the main parameter file \texttt{Par\_file}, which resides in the subdirectory \texttt{in\_data\_files/}. Please note that  
\texttt{xgenerate\_databases} must be called directly from the \texttt{bin/} directory, as most of the binaries of the package.
Before running \texttt{xgenerate\_databases}, a number of parameters need to be set in the \texttt{Par\_file}:

@@

Now that you have successfully generated the databases, you are ready to compile
the solver. In the main directory type `\texttt{make specfem3D}'.
Please note that \texttt{xspecfem3D} must be called directly from 
the \texttt{bin/} directory, as most of the binaries of the package.

%obsolete
%For reasons of speed, the solver uses static memory allocation.
%Therefore it needs to be recompiled (type `\texttt{make clean}' and
%`\texttt{make specfem3D}') every time one reruns \texttt{xgenerate\_databases}. To compile
%the solver one needs a file created by \texttt{xgenerate\_databases} in the directory
%\texttt{OUTPUT\_FILES} called \texttt{values\_from\_mesher.h}, which
%contains parameters describing the static size of the arrays as well
%as the setting of certain flags.
